---
title: Tuango - RFM Analysis for Mobile App Push Messaging on the post roll-out data
output: html_document
---

* Name: Ziyuan Yan
* GitLab id: @rsm-ziy062

```{r r_setup, include = FALSE}
## initial settings
knitr::opts_chunk$set(
  comment = NA,
  echo = TRUE,
  error = TRUE,
  cache = FALSE,
  message = FALSE,
  dpi = 96,
  warning = FALSE
)

## width to use when printing tables etc.
options(
  width = 250,
  scipen = 100,
  max.print = 5000,
  stringsAsFactors = FALSE
)

## make all required libraries available by loading radiant package if needed
if (!exists("r_environment")) library(radiant)
```

<style>
.btn, .form-control, pre, code, pre code {
  border-radius: 4px;
}
.table {
  width: auto;
}
ul, ol {
  padding-left: 18px;
}
code, pre, pre code {
  overflow: auto;
  white-space: pre;
  word-wrap: normal;
}
code {
  color: #c7254e;
  background-color: #f9f2f4;
}
pre {
  background-color: #ffffff;
}
</style>

## Setup

Please complete this Rmarkdown document by answering question 14 in `tuango.pdf` on Canvas (week4/). The code block below loads the data you need for this second Rmarkdown file. Create an HTML file with all your results and answers and push both the Rmarkdown and HTML file to GitLab when you are done. All results MUST be reproducible (i.e., the TA and I must be able to recreate the Notebook/HTML from the Rmarkdown file without changes or errors).

```{r}
library(tidyverse)
library(radiant)
```

```{r}
## loading the data - this dataset must NOT be changed
tuango_post <- readr::read_rds("data/tuango_post.rds")
```

### Question 14
```{r}
training <- filter(tuango_post, training == 1)

avgSpent <- mean(filter(training, ordersize!=0)$ordersize)

cost_offer <- 2.5
margin_sales <- avgSpent * 0.5
break_even <- cost_offer/margin_sales # Use training == 1 to calculate break_even rate
```

```{r}
# independent quntile
tuango_post <- tuango_post %>%
  mutate(rec_iq = xtile(recency, n = 5), 
         freq_iq = xtile(frequency, n = 5, rev = TRUE),
         mon_iq = xtile(monetary, n = 5, rev = TRUE))
```

```{r}
tuango_post <- mutate(tuango_post, rfm_iq = paste0(rec_iq, freq_iq, mon_iq))
identical(tuango_post$rfm_iq_pre, tuango_post$rfm_iq)
```

```{r}
# sequential quntile
tuango_post <- tuango_post %>%
  group_by(rec_iq) %>%
  mutate(freq_sq = xtile(frequency, n = 5, rev = TRUE)) %>%
  ungroup()

tuango_post <- tuango_post %>%
  group_by(rec_iq, freq_sq) %>%
  mutate(mon_sq = xtile(monetary, n = 5, rev = TRUE)) %>%
  ungroup()

tuango_post <- tuango_post %>%
  mutate(rfm_sq = paste0(rec_iq, freq_sq, mon_sq))
```

```{r}
remaining <- tuango_post %>%
  filter(training == 0)

# Function
perf_calc <- function(index, match, intro) {
  count <- 0
  sales <- 0
  for (i in 1:250902) {
    if (remaining[[index]][i] %in% match) {
      count <- count + 1
      sales <- sales + (remaining$ordersize[i] * 0.5)
    }
  }
  costs <- count * cost_offer
  profit <- sales - costs
  ROME <- profit / costs
  return(c(profit, ROME, paste0(intro, ", the cost is ", round(costs, 2), "RMB, the profit is ", round(profit, 2), "RMB, and the ROME is ", ROME, ".")))
}
```

#### Method 1: Independent RFM
```{r}
indep <- tuango_post %>%
  filter(training == 1) %>%
  group_by(rfm_iq) %>%
  mutate(smsto_iq = mean(buyer == "yes") > break_even) %>%
  filter(smsto_iq == TRUE) %>%
  ungroup()

RFM_Ind <- perf_calc(index = "rfm_iq", match = indep$rfm_iq, intro = "Based on independent RFM")
RFM_Ind
```

#### Method 2: Sequential RFM
```{r}
seq <- tuango_post %>%
  filter(training == 1) %>%
  group_by(rfm_sq) %>%
  mutate(smsto_sq = mean(buyer == "yes") > break_even) %>%
  filter(smsto_sq == TRUE) %>%
  ungroup()

RFM_Seq <- perf_calc(index = "rfm_sq", match = seq$rfm_sq, intro = "Based on sequential RFM")
RFM_Seq
```

#### Method 3: Sequential RFM based on a breakeven response rate calculated for each RFM cell.
```{r}
# calculate break-even rate for every cell in the training set
indiv_be <- tuango_post %>%
  filter(training == 1) %>%
  filter(buyer == "yes") %>%
  group_by(rfm_sq) %>%
  summarise(avg_ordersize = mean(ordersize)) %>%
  mutate(breakeven_indiv = cost_offer / (avg_ordersize * 0.5))

be2 <- tuango_post %>%
  filter(training == 1) %>%
  left_join(indiv_be, by = "rfm_sq") %>%
  group_by(rfm_sq) %>%
  mutate(smsto_sq_indiv_be = mean(buyer == "yes") > breakeven_indiv) %>%
  filter(smsto_sq_indiv_be == TRUE) %>%
  ungroup()

RFM_Seq_indiv_be <- perf_calc(index = "rfm_sq", match = be2$rfm_sq, intro = "Based on sequential RFM with a breakeven response rate for each RFM index")
RFM_Seq_indiv_be
```

#### Method 4: Calculate the performance based on the independent RFM with adjusting for the standard error of the response rate
```{r}
Ind_lb <- tuango_post %>%
  filter(training == 1) %>%
  group_by(rfm_iq) %>%
  mutate(smsto_lbiq = (mean(buyer == "yes") - 1.64 * seprop(buyer == "yes")) > break_even) %>%
  filter(smsto_lbiq == TRUE) %>%
  ungroup()

RFM_Ind_lb <- perf_calc(index = "rfm_iq", match = Ind_lb$rfm_iq, intro = "Based on independent RFM with adjusting for the standard error of the response rate")
RFM_Ind_lb
```

#### Method 5: Calculate the performance based on the sequential RFM with adjusting for the standard error of the response rate
```{r}
Seq_lb <- tuango_post %>%
  filter(training == 1) %>%
  group_by(rfm_sq) %>%
  mutate(smsto_lbsq = (mean(buyer == "yes") - 1.64 * seprop(buyer == "yes")) > break_even) %>%
  filter(smsto_lbsq == TRUE) %>%
  ungroup()

RFM_Seq_lb <- perf_calc(index = "rfm_sq", match = Seq_lb$rfm_sq, intro = "Based on sequential RFM with adjusting for the standard error of the response rate")
RFM_Seq_lb
```

```{r}
# Make a tibble containing profit and ROME
Q14 <- tibble::tibble(
  name = c("Indep RFM", "Sequen RFM", "Indiv BE RFM", "Indep lb RFM", "Seq lb RFM"),
  Profit = c(as.numeric(RFM_Ind[1]), as.numeric(RFM_Seq[1]), as.numeric(RFM_Seq_indiv_be[1]), as.numeric(RFM_Ind_lb[1]), as.numeric(RFM_Seq_lb[1])),
  ROME = c(as.numeric(RFM_Ind[2]), as.numeric(RFM_Seq[2]), as.numeric(RFM_Seq_indiv_be[2]), as.numeric(RFM_Ind_lb[2]), as.numeric(RFM_Seq_lb[2]))
) %>%
  mutate(name = factor(name, levels = name))
```

```{r}
ggplot(Q14, aes(x = name, y = Profit)) + 
  geom_bar(stat = 'identity') + 
  geom_text(aes(label = format_nr(Profit, dec = 0)), vjust = 2) +
  labs(title = "Pofit information for 5 methods")
```

```{r}
ggplot(Q14, aes(x = name, y = ROME)) + 
  geom_bar(stat = 'identity') + 
  geom_text(aes(label = format_nr(ROME, dec = 2)), vjust = 2) +
  labs(title = "ROME information for 5 methods")
```





